Are We Reusing Outdated and Licensed Code from Stack Overflow?

### 2017-02-14 cloneoverflow-latex/cloneoverflow.tex
Consistency checks, English checks, numbers check + improvements throughout the paper.

\documentclass[sigconf]{acmart}

@@

\textbf{Stack Overflow}: we extracted Java code snippets from a snapshot of a Stack Overflow dump\footnote{https://archive.org/details/stackexchange} in January 2016. The archived dump has a size of 9 gigabytes. The data dump was in XML format containing information of \textbf{Posts} (questions and answers) and supporting data such as user accounts and timestamps of the posts. We were interested in code snippets embedded in posts which were located between {\small\texttt{<code></code>}} tags. A Stack Overflow thread contains a post of question and several posts of answers. Every answer has voting score from its users. An answer can also be marked as \textbf{accepted answer} by the questioner if the solution fixes his/her problem. We collected Java code snippets using two criteria. First, we were only interested in code snippets with at least six lines. Snippets which were smaller than six lines were usually spurious clones~\cite{Bellon2007}. Second, we only focused on code snippets in accepted answers. We chose the snippets in accept answers because they actually solved the problems in the questions and had a check mark sign on them to notify other users. Moreover, they were always displayed just below the questions which made them attractive to be reused than other answers. Each snippet was extracted from the dump using regular expressions and saved to a file using its post ID as the file's name. If an accepted answer had more than one code snippet, we appended an indexing number, starting from zero, after the post ID (e.g. 45051109\_0, and 45051109\_1.). Lastly, we added {\small\texttt{.java}} extension to the file's names so that clone detectors could recognise them. We finally obtained 144,075 Java code snippets which contain 2,347,269 lines of Java source code excluding comments and blank lines\footnote{Measured by cloc: https://github.com/AlDanial/cloc}.

\textbf{Open source systems}: we selected an established corpus for an empirical software engineering study called \textbf{Qualitas}~\cite{QualitasCorpus} for this study. It is a curated Java corpus that has been used in several software engineering studies~\cite{Taube-Schock2011,Beckman2011,Vasilescu2011,Omar2012}. The projects in the corpus represent various domains of software systems ranging from programming language to 3D and visualisation~\cite{QualitasCorpus}. We selected the 20130901r release of Qualitas corpus containing 112 Java open source projects. This release contains projects with releases no later than 1st September 2013. We chose a snapshot late back in 2013 since we are interested in online code clones in the direction from open source projects to Stack Overflow. The 20130901r snapshot provides Java code that is at least 3 years old from the time of the experiment (January to December 2016). The time difference is sufficiently long for a number of code snippets to be copied onto Stack Overflow. Out of 112 Qualitas projects, there is one project, \texttt{jre}, that does not contain Java source code due to its licensing limitation~\cite{QualitasCorpus} so it is removed from the study. This resulted in total of 111 projects analysed in the study. As shown in \Cref{tab:datasets}, the 111 Qualitas project have 160,937 Java files containing 19,086,883 lines of code. %Details of the 109 Qualitas projects and their licenses are listed in Table \ref{t:new_and_old}.

@@

\subsubsection{Clone Detectors}
There is a number of restrictions in terms of choosing clone detection tools for this study. First, they have to support Java. Second, due to nature of code snippets posted on Stack Overflow, some of them are not complete Java classes or methods. Hence, the tool must be flexible enough to process code snippets that are neither a complete block nor compilable. Third, since the amount of code that have to be processed are in a scale of millions line of code (as shown in \Cref{tab:datasets}), a clone detector must be scalable enough to successfully complete the execution and report clones in a reasonable amount of time. We have tried running 5 state-of-the-art clone detectors including Simian~\cite{simian}, NiCad~\cite{Cordy,Roy2008}, CCFinder~\cite{Kamiya2002}, iClones~\cite{Gode2009}, and DECKARD~\cite{Jiang2007a} against Stack Overflow and Qualitas datasets. CCFinder, iClones, and DECKARD failed to report clones between 144,075 Stack Overflow code snippets and 111 Qualitas projects. All of them reported execution errors after running for couple of hours. Thus, we removed them from the study. Simian and NiCad completed the detection with success. We found that both of them are also flexible enough to handle code with incomplete methods or classes. %So, we decided to use both of them.

\textbf{Simian} is a text-based clone detector which locate clones at line-level granularity and has been used extensively in several clone studies~\cite{Ragkhitwetsagul2016, Wang2013, Mondal2011, Cheung2015, Krinke2010}. It is a command-line tool which enables us to automate the detection. Furthermore, it offers normalisation of variable names and literals (strings, and numbers) which enable Simian to detect literal clones (type-1) and parameterised clones (type-2). \textbf{NiCad} is also a text-based clone detector which detects clones at either method- or block-level granularity. It can detect clones of type-1, 2 up to type-3 (clones with added/removed/relocated/changed statements) and is also used in several empirical clone studies~\cite{Roy2008, Ragkhitwetsagul2016, Svajlenko2014, Wang2013, Mondal2011, Sajnani2016}. It utilises TXL~\cite{Cordy2006} for parsing and pretty-printing source code. It also provide code normalisation by variable renaming and abstraction. We use a variant of NiCad called \textit{nicadcross}. It offers the same functionalities as the original NiCad but is specialised for detecting code clones between two systems. NiCad is also a command-line tool which makes it suitable for automation.

\subsubsection{Prioritise Clone Candidates Using Agreement}
A number of clones detected in large-scale datasets can be huge. In our study, there are totally 266,837,480 clone pairs reported. It is almost infeasible for human to manually validate them all. One can do a random sampling of clones. However, due to a very high number of false positives, they may end up looking at most of the false clones. Therefore, we adopted an idea of \textbf{clone agreement} which has been used in clone research studies~\cite{Wang2013,Funaro2010,cr2016ssbse} in a situation that clone oracle is missing or impossible to establish. Clone pairs agreed by multiple clone detection tools have higher confident to be real clones~\cite{cr2016ssbse}. By using this agreement-based approach, we could reduce the number of clone candidates for manual investigation by paying more attention to the ones agreed by multiple tools. To find an agreement between two clone pairs report by two different tools, we used clone pair matching metric proposed by Bellon et al.~\cite{Bellon2007}. Two clone pairs which have large enough overlapping clone lines can be categorised as either a good-match or an ok-match pair (denoted as \textit{good} and \textit{ok} respectively) with a confident value between 0 and 1. A \textit{good} clone pair has stronger agreement than an \textit{ok} pair. We follow the following definitions of good- and ok-match introduced in the original paper.

@@

Two clone pairs $\textrm{\textit{CP}}_1$ and $\textrm{\textit{CP}}_2$ are called a \textit{\textit{good}(p)} iff, for $p \in [0,1]$ holds 
%\squeezeup
\begin{equation}
good(\textrm{\textit{CP}}_1,\textrm{\textit{CP}}_2) \geq p.
\end{equation}

@@

Using this good and ok-match criteria with a predefined threshold \textit{p}, we can prune the 266-million candidate clone pairs for manual investigation. \textit{good} pairs are the ones with the highest confident and ranked the first to be looked at, followed by \textit{ok} pairs, and followed by clone pairs without agreement.

\subsection{Clone Detector's Parameter Tuning}
We were aware of effects of configurations to clone detection results and the importance of searching for optimised configurations in empirical clone studies~\cite{Wang2014,cr2016ssbse,Ragkhitwetsagul2016,Svajlenko2014}. However, considering the massive size of the two datasets and search space of at least 15 Simian's and 5 NiCad's parameters, we were hindered from searching for the best configurations of the tools. Thus, we decided to configure Simian and NiCad using two established configurations: 1) the tools' default configurations chosen by the tools' creators (denoted as \textit{D}), and 2) the discovered configurations for Bellon's Java projects from \textit{EvaClone}, a study of optimising clone detectors' configurations based on clone agreement, by Wang et al.~\cite{Wang2013} (denoted by \textit{E}). The details of the two configurations are described in \Cref{t:param_tuning}. Having two clone detectors, Simian (denoted as \textit{S}) and NiCad (denoted as \textit{N}), with two chosen configurations each, we looked for Bellon's good and ok-match in four possible pair-wise combinations: $S_{D}N_{D}$, $S_{D}N_{E}$, $S_{E}N_{D}$, and $S_{E}N_{E}$.

@@

We followed the experimental framework and detected clones between Stack Overflow and Qualitas corpus using the two selected clone detectors. To answer RQ1, we computed statistics of clone discovered by the tools. To answer RQ2, we manually investigated online clone pair candidates and categorised them using our patterns of online code cloning. The patterns were derived from Kapser et al.~\cite{Kapser2003} augmented by common patterns found in our data set. For RQ3, we looked at the true positive clone pairs and check if they are still up-to-date. Similarly, for RQ4, we also looked at the license of each clone and observed a possibility of licensing violation.

@@

The clone statistics obtained from running Simian and NiCad with \textit{D} and \textit{E} configurations are presented in \Cref{tab:raw_stats}. From \Cref{tab:raw_stats}, Simian clones cover approximately 1\% of the 144,075 Stack Overflow snippets, 1,086 reported by $S_D$ and 1,531 from $S_E$ respectively. $N_D$ reports clones in 1,392 Stack Overflow code snippets, while $N_E$ reports clones in a larger number of 12,886 snippets  mainly due to its relaxed configurations. In terms of number of clone pairs, $S_E$ and $N_E$ report a large number of clone pairs of 63,635,844 and 251,449,849 respectively. This is expected since EvaClone configurations prefer recall so it tends to remote more clones~\cite{Wang2013}. The average clone size of $S_D$ is 7.72 lines which is bigger than its $S_E$ counterpart of 4.79. Similarly, $N_D$ has an average clone size of 9.84 lines which is bigger than 5.33 reported by $N_E$. We can see from the statistics that EvaClone tunes the tools in the way that they report smaller clones. The average percentage of Stack Overflow code snippets that are cloned according to $S_D$, $S_E$, $N_D$, and $N_E$ is 29\%, 28\%, 25\%, and 21\% accordingly. A quick manual check of Simian's clone report revealed that there were problematic 11 snippets. These 11 snippets triggered Simian to generate large clone clusters containing a huge number of false clones from array initialisation. Hence, their clones were removed from further analyses.

As displayed in \Cref{tab:online_clone_pairs}, after we applying clone agreement filtering using Bellon's criteria, the number of \textit{good} agreed clone pairs is 2,308 while \textit{ok} is 11,749. The number of disagreed clone pairs ($S_D$, $N_D$) after filtering is 17,801 and 181 for Simian and NiCad respectively. The total number of clone candidates is 32,039 pairs. The details are as follows.

\begin{table}
	\centering
	\caption{The number of online clone pair condidates (mutually exclusive) before and after filtering.}
	\label{tab:online_clone_pairs}
	\small
%	\resizebox{\columnwidth}{!}{%
	\begin{tabular}{l|r|c|c|c|c|r}
		\hline
		\multirow{2}{*}{Set} & \multicolumn{1}{c|}{Before} & \multicolumn{4}{c|}{Filters*} & \multirow{2}{*}{Cand.} \\ \cline{3-6}
		& \multicolumn{1}{c|}{Filters} & \textit{L} & \textit{S} & \textit{R} & \textit{G} & \\
		\hline 
		\multirow{1}{*}{\textit{good}} & 2,308 & & & & & 2,308 \\
		\multirow{1}{*}{\textit{ok}} & 11,749 & & & & & 11,749 \\
		%\multirow{1}{*}{\textit{agreed clone pairs}}      & 29,099 \\
		\multirow{1}{*}{$S_D$} & 67,570 & \checkmark & & \checkmark & \checkmark & 17,801 \\
		\multirow{1}{*}{$N_D$} & 229,176 & & \checkmark & \checkmark & \checkmark & 88 \\ 
		%\multirow{1}{*}{\textit{disagreed clone pairs}}    & 1,039 \\
		\hline
		Total  & 310,803 & & & & & 31,946 \\ 
		\hline
		\multicolumn{7}{l}{Filters*: \textit{L}=$Line \geq 10$, \textit{S}=$Sim \geq 85\%$,} \\
		\multicolumn{7}{l}{\textit{R}=regular expressions, and \textit{G}=\textit{good}/\textit{ok} pairs.} \\
	\end{tabular} %
%}
\end{table}

\begin{table}
	\centering
	\caption{The online clone classification results}
	\label{tab:online_clone_classification_results}
	\small
	%	\resizebox{\columnwidth}{!}{%
	\begin{tabular}{l|r|r|r|r}
		\hline
		\multirow{2}{*}{Set} & \multirow{2}{*}{Candidates} & \multicolumn{2}{c|}{Classification} & \multirow{2}{*}{TP} \\ \cline{3-4}
		& & Auto & Manual & \\
		\hline 
		\multirow{1}{*}{\textit{good}} & 2,308 & 10 & 2,298 & 18 \\
		\multirow{1}{*}{\textit{ok}} & 11,749 & 11,494 & 255 & 75 \\
		%\multirow{1}{*}{\textit{agreed clone pairs}}      & 29,099 \\
		\multirow{1}{*}{$S_D$} & 17,801 & 16,800 & 1,001 & 525 \\
		\multirow{1}{*}{$N_D$} & 88 & 10 & 78 & 50 \\ 
		%\multirow{1}{*}{\textit{disagreed clone pairs}}    & 1,039 \\
		\hline
		Total  & 31,946 & 28,314 & 3,632 & 668 \\ 
		\hline
	\end{tabular} %
	%}
\end{table}

@@

Agreed clone pairs are clone pairs that pass Bellon's good- or ok-match criteria and selected for manual investigation. Similar to the original study, we select a threshold \textit{p} of 0.7 for both \textit{good} and \textit{ok} pairs~\cite{Bellon2007}. %The number of projects processed by the clone detection tools are listed in \Cref{tab:projects_missing}. 
We encountered NiCad failures with a few Qualitas projects.~$N_D$ could not detect clones in \texttt{hibernate} due to clustering errors. $N_E$ generated renaming errors for 5 projects including \texttt{vuze}, \texttt{hibernate}, \texttt{myfaces}, \texttt{netbeans}, and \texttt{spring}. We had contacted the creator of NiCad regarding the issues. They identified them as problems of long file paths and TXL grammars which will be fixed in the next NiCad releases. As a result, we did not have NiCad clones from these projects in the agreed clone pairs. Simian clones of the same projects also disappeared from the agreed clone pairs since they could not find matches.

@@

The distributions of \textit{good} clone pairs between four combinations of \textit{D} and \textit{E} configurations are listed in \Cref{t_agreed_good_clone_pairs} and depicted visually in \Cref{fig:good-ok-pairs}. There are 2,321 (2,308 unique) \textit{good} pairs consisting of 18 pairs from $S_DN_D$, 26 pairs from $S_DN_E$, 10 pairs from $S_EN_D$, and 2,267 pairs from $S_EN_E$. There are 32,560 (11,749 unique) \textit{ok} pairs\footnote{This excludes the subsumed 2,308 \textit{good} pairs. According to the definition, \textit{ok} pairs always subsume \textit{good} pairs.} We obtained 11,467; 993; 79; and 20,021 pairs from $S_DN_D$, $S_DN_E$, $S_EN_D$, and $S_EN_E$ respectively. Between the four configuration sets, there are considerable amount of clone pairs shared between two adjacent sets (as depicted in \Cref{fig:good-ok-pairs}), but there is no clone pair that is agreed by all four combinations.

@@

The disagreed clone pairs are clone pairs that are reported by a single tool, either Simian or NiCad, and do not have agreement with clones from another tool. The disagreement can be from misalignment of clone lines or totally dissimilar clones due to different configurations. Disagreed pairs from Simian also cover clone pairs in projects having NiCad's errors (1 projects for $N_D$ and 5 for $N_E$) that are automatically missing from the agreed clone pairs. With the four configuration combinations, we decided to investigate only $S_D$, and $N_D$, and drop $S_E$ and $N_E$ due to their enormous amount of clone pairs (60 and 250 millions respectively). Moroever, without clone agreement, $S_E$ and $N_E$ contain a large number of false positives due to the recall preference of their EvaClone configurations.

Even choosing only the default configurations, the number of clone pair candidates are still very large for manual inspection (67,570 for $S_D$ and 229,176 pairs for $N_D$). We hence apply four filters: \textbf{clone size, regular expression, similarity threshold, and good/ok pairs}. For the clone size filter, we raise the minimum clone size to 10 line as larger clones tend to be more interesting while smaller ones tend to be false clones~\cite{Saini2016}. Moreover, Gabel and Su show that unique code tend to be larger than seven lines~\cite{Gabel2010}. The 10--line threshold is already the default configuration for NiCad, thus this filter affects Simian clones only (Simian's default configurations consider a minimum of 6 lines).~The regular expression filter captures uninteresting boiler-plate clones of \verb|hashCode()| methods and some of the obvious getters and setters using regular expressions and removes them. The third filter, similarity threshold, applies only to NiCad clone pairs since Simian does not provide this similarity threshold configuration. The last filter, good/ok pairs, filters the pairs that already exist in \textit{good} or \textit{ok} set to avoid duplicates.

As shown in \Cref{tab:online_clone_pairs}, for $S_D$ we filtered the results using clone size, regular expressions, and gook/ok pairs. The combination of the three filters reduce the number of $S_D$ clones to 17,801 pairs for manual investigation. 
For $N_D$, 10-line threshold is already a minimum NiCad's clone size. However, NiCad still reported much more clone pairs than Simian since it can detect type-3 clones. Thus, besides regular expressions and good/ok pair filters, we filtered NiCad's clones further by a stricter similarity threshold. We increase NiCad's similarity threshold from 70\% to 85\% (by adjusting NiCad's $\mathrm{UPI}$ from 0.3 to 0.15). We have tried varying the UPI from 70\% (default), 80\%, 85\% and 90\% and we found that 85\% similarity provides the best balance in terms of the amount of reported clones and feasibility for manual investigation. Using the three filters, we reduced the size of $N_D$ clones to 88 pairs.

In our clone classification process, we used a script to automatically classify {\small\texttt{equals()}} clone pairs which helped classifying 28,444 pairs out of 31,946 (more than half of the {\small\texttt{equals()}} pairs came from \textit{ok} and $S_D$ pairs). Finally, there are 3,502 pairs remaining which we manually classified them. The classification summary is shown in \Cref{tab:online_clone_classification_results}.

\textbf{To answer RQ1, we found 31,946 clone candidates between 111 Qualitas projects and 144,075 Stack Overflow snippets. They are 2,308 \textit{good}, 11,749 \textit{ok}, 17,801 $S_D$, and 88 $N_D$ pairs. After classification, we found 668 non-trivial online code clones pairs between Stack Overflow and Qualitas or external sources.}

>>>>

\documentclass[sigconf,review, anonymous]{acmart}

@@

\textbf{Stack Overflow}: we extracted Java code snippets from a snapshot of a Stack Overflow dump\footnote{https://archive.org/details/stackexchange} in January 2016. The archived dump has a size of 9 gigabytes. The data dump was in XML format containing information of \textbf{Posts} (questions and answers) and supporting data such as user accounts and timestamps of the posts. We were interested in code snippets embedded in posts which were located between {\small\texttt{<code></code>}} tags. A Stack Overflow thread contains a post of a question and several posts of answers. Every answer has voting score from its users. An answer can also be marked as \textbf{accepted answer} by the questioner if the solution fixes his/her problem. We collected Java code snippets using two criteria. First, we were only interested in code snippets with at least six lines. Snippets that are smaller than six lines are usually spurious clones~\cite{Bellon2007}. Second, we only focused on code snippets in accepted answers. We chose the snippets in accepted answers because they actually solved the problems in the questions. Moreover, they are always displayed just below the questions which makes them attractive to be reused than other answers. Each snippet was extracted from the dump and saved to a file. 
%using its post ID as the file's name. If an accepted answer had more than one code snippet, we appended an indexing number, starting from zero, after the post ID (e.g. 45051109\_0, and 45051109\_1.). Lastly, we added {\small\texttt{.java}} extension to the file's names so that clone detectors could recognise them. 
We obtained 144,075 Java code snippets which contain 2,347,269 lines of Java source code excluding comments and blank lines\footnote{Measured by cloc: https://github.com/AlDanial/cloc}.

\textbf{Open source systems}: we selected an established corpus for an empirical software engineering study called \textbf{Qualitas}~\cite{QualitasCorpus} for this study. It is a curated Java corpus that has been used in several software engineering studies~\cite{Taube-Schock2011,Beckman2011,Vasilescu2011,Omar2012}. The projects in the corpus represent various domains of software systems ranging from programming languages to visualisation~\cite{QualitasCorpus}. We selected the 20130901r release of Qualitas corpus containing 112 Java open source projects. This release contains projects with releases no later than 1st September 2013. We chose a snapshot late back in 2013 since we are interested in online code clones in the direction from open source projects to Stack Overflow. The 20130901r snapshot provides Java code that is at least 3 years old from the time of the experiment (January to December 2016). The time difference is sufficiently long for a number of code snippets to be copied onto Stack Overflow. Out of 112 Qualitas projects, there is one project, \texttt{jre}, that does not contain Java source code due to its licensing limitation~\cite{QualitasCorpus} so it is removed from the study. This resulted in a total of 111 projects analysed in the study. As shown in \Cref{tab:datasets}, the 111 Qualitas project have 160,937 Java files containing 19,086,883 lines of code. %Details of the 109 Qualitas projects and their licenses are listed in Table \ref{t:new_and_old}.

@@

\subsubsection{Clone Detectors}
There is a number of restrictions in terms of choosing clone detection tools for this study. The main restriction is due to nature of code snippets posted on Stack Overflow, most of them are not complete Java classes or methods. Hence, the tool must be flexible enough to process code snippets that are neither a complete block nor compilable. Moreover, since the amount of code that has to be processed is in a scale of millions line of code (as shown in \Cref{tab:datasets}), a clone detector must be scalable enough to successfully complete the execution and report clones in a reasonable amount of time. We have tried running 5 state-of-the-art clone detectors including Simian~\cite{simian}, NiCad~\cite{Cordy,Roy2008}, CCFinder~\cite{Kamiya2002}, iClones~\cite{Gode2009}, and DECKARD~\cite{Jiang2007a} against Stack Overflow and Qualitas datasets. CCFinder, iClones, and DECKARD failed with execution errors after running for couple of hours. Thus, we removed them from the study. Simian and NiCad completed the detection with success. We found that both of them are also flexible enough to handle code with incomplete methods or classes. %So, we decided to use both of them.

\textbf{Simian} is a text-based clone detector that locates clones at line-level granularity and has been used extensively in several clone studies~\cite{Ragkhitwetsagul2016, Wang2013, Mondal2011, Cheung2015, Krinke2010}. It is a command-line tool which enables us to automate the detection. Furthermore, it offers normalisation of variable names and literals (strings, and numbers) which enable Simian to detect literal clones (type-1) and parameterised clones (type-2). \textbf{NiCad} is also a text-based clone detector which detects clones at either method- or block-level granularity. It can detect clones of type-1, 2 up to type-3 (clones with added/removed/relocated/changed statements) and is also used in several empirical clone studies~\cite{Roy2008, Ragkhitwetsagul2016, Svajlenko2014, Wang2013, Mondal2011, Sajnani2016}. It utilises TXL~\cite{Cordy2006} for parsing and pretty-printing source code. It also provides code normalisation by variable renaming and abstraction. We use a variant of NiCad called \textit{nicadcross}. It offers the same functionalities as the original NiCad but is specialised for detecting code clones between two systems. NiCad is also a command-line tool which makes it suitable for automation.

\subsubsection{Prioritise Clone Candidates Using Agreement}
The number of clones detected in large-scale datasets can be huge. In our study, there are in total 266,837,480 clone pairs reported. It is infeasible for humans to manually validate them all. One can do a random sampling of clones. However, due to a very high number of false positives, they may end up looking at most of the false clones. Therefore, we adopted the idea of \textbf{clone agreement} which has been used in clone research studies~\cite{Wang2013,Funaro2010,cr2016ssbse} in situations where a clone oracle is missing or impossible to establish. Clone pairs agreed by multiple clone detection tools have a higher confidence to be real clones~\cite{cr2016ssbse}. By using this agreement-based approach, we could reduce the number of clone candidates for manual investigation by paying more attention to the ones agreed by multiple tools. To find an agreement between two clone pairs report by two different tools, we used the clone pair matching metric proposed by Bellon et al.~\cite{Bellon2007}. Two clone pairs which have a large enough number of overlapping clone lines can be categorised as either a good-match or an ok-match pair (denoted as \textit{good} and \textit{ok} respectively) with a confident value between 0 and 1. A \textit{good} clone pair has stronger agreement than an \textit{ok} pair. We follow the following definitions of good- and ok-match introduced in the original paper.

@@

Two clone pairs $\textrm{\textit{CP}}_1$ and $\textrm{\textit{CP}}_2$ are called a \textit{\textit{good}(p)} iff, for threshold $p \in [0,1]$ holds 
%\squeezeup
\begin{equation}
good(\textrm{\textit{CP}}_1,\textrm{\textit{CP}}_2) \geq p.
\end{equation}

@@

Using this good and ok-match criteria with a predefined threshold \textit{p}, we can prune the 266 million candidate clone pairs for manual investigation. \textit{good} pairs are the ones with the highest confident and ranked first to be looked at, followed by \textit{ok} pairs, and followed by clone pairs without agreement.

\subsection{Clone Detector's Parameter Tuning}
We were aware of effects of configurations to clone detection results and the importance of searching for optimised configurations in empirical clone studies~\cite{Wang2014,cr2016ssbse,Ragkhitwetsagul2016,Svajlenko2014}. However, considering the massive size of the two datasets and search space of at least 15 Simian and 5 NiCad parameters, we were hindered from searching for the best configurations of the tools. Thus, we decided to configure Simian and NiCad using two established configurations: 1) the tools' default configurations chosen by the tools' creators (denoted as \textit{D}), and 2) the discovered configurations for Bellon's Java projects from \textit{EvaClone}, a study of optimising clone detectors' configurations based on clone agreement, by Wang et al.~\cite{Wang2013} (denoted by \textit{E}). The details of the two configurations are described in \Cref{t:param_tuning}. Having two clone detectors, Simian (denoted as \textit{S}) and NiCad (denoted as \textit{N}), with two chosen configurations each, we looked for Bellon's good and ok-match in four possible pair-wise combinations: $S_{D}N_{D}$, $S_{D}N_{E}$, $S_{E}N_{D}$, and $S_{E}N_{E}$.

@@

We followed the experimental framework and detected clones between Stack Overflow and Qualitas corpus using the two selected clone detectors. To answer RQ1, we computed statistics on clones discovered by the tools. To answer RQ2, we manually investigated online clone pair candidates and categorised them using our patterns of online code cloning. The patterns were derived from Kapser et al.~\cite{Kapser2003} augmented by common patterns found in our data set. For RQ3, we looked at the true positive clone pairs and checked if they are still up-to-date. Similarly, for RQ4, we also looked at the license of each clone and checked for a possibility of licensing violation.

@@

The clone statistics obtained from running Simian and NiCad with \textit{D} and \textit{E} configurations are presented in \Cref{tab:raw_stats}. Simian clones cover approximately 1\% of the 144,075 Stack Overflow snippets, 1,086 reported for $S_D$ and 1,531 for $S_E$ respectively. $N_D$ reports clones in 1,392 Stack Overflow code snippets, while $N_E$ reports clones in a much larger number of 12,886 snippets  mainly due to its relaxed configurations. In terms of number of clone pairs, $S_E$ and $N_E$ report a large number of clone pairs, 63,635,844 and 251,449,849 respectively. This large number of clones is expected since EvaClone configurations prefer recall~\cite{Wang2013}. $S_D$ and $N_D$ have the average clone pairs per snippet of 62 and 455 respectively. On the other hand, $S_E$ and $N_E$ have a much larger number of 63 and 251 million clone pairs per snippet on average. The average clone size of $S_D$ is 7.72 lines which is bigger than its $S_E$ counterpart of 4.79. Similarly, $N_D$ has an average clone size of 9.84 lines which is bigger than 5.33 reported by $N_E$. We can see from the statistics that EvaClone tunes the tools in a way that they report smaller clones. The average ratio of Stack Overflow code snippets that are cloned according to $S_D$, $S_E$, $N_D$, and $N_E$ is 29\%, 28\%, 25\%, and 21\% accordingly. A quick manual check of Simian's clone report revealed that there were 11 problematic snippets. These 11 snippets triggered Simian to generate large clone clusters containing a huge number of false clones from array initialisation. Hence, their clones were removed from further analyses.

As displayed in \Cref{t_agreed_good_clone_pairs}, after we applying clone agreement filtering using Bellon's criteria, the number of \textit{good} clone pairs is 2,308 while the number of \textit{ok} clone pairs is 31,729. %The number of disagreed clone pairs ($S_D$, $N_D$) after filtering is 17,801 and 181 for Simian and NiCad respectively. The total number of clone candidates is 32,039 pairs. 
We explain them in more details below.

@@

Agreed clone pairs are clone pairs that pass Bellon's \textit{good} or \textit{ok} criteria and selected for manual classification. Similar to the original study, we select a threshold \textit{p} of 0.7 for both \textit{good} and \textit{ok} pairs~\cite{Bellon2007}. %The number of projects processed by the clone detection tools are listed in \Cref{tab:projects_missing}. 
We encountered NiCad failures with a few Qualitas projects.~$N_D$ could not detect clones in \texttt{hibernate} due to clustering errors. $N_E$ generated renaming errors for 5 projects including \texttt{vuze}, \texttt{hibernate}, \texttt{myfaces}, \texttt{netbeans}, and \texttt{spring}. We had contacted the creator of NiCad regarding the issues. They identified them as problems of long file paths and TXL grammars which will be fixed in the next NiCad releases. As a result, we did not have NiCad clones from these projects in the agreed clone pairs. Simian clones of the same projects also disappeared from the agreed clone pairs since they could not find matches.

@@

The distributions of \textit{good} clone pairs between four combinations of \textit{D} and \textit{E} configurations are listed in \Cref{t_agreed_good_clone_pairs}. %and depicted visually in \Cref{fig:good-ok-pairs}. 
There are 2,321 (2,308 unique) \textit{good} pairs consisting of 18 pairs from $S_DN_D$, 26 pairs from $S_DN_E$, 10 pairs from $S_EN_D$, and 2,267 pairs from $S_EN_E$. There are 32,560 (31,729 unique) \textit{ok} pairs\footnote{This excludes the subsumed 2,308 \textit{good} pairs. According to the definition, \textit{ok} pairs always subsume \textit{good} pairs.} We obtained 11,467; 993; 79; and 20,021 pairs from $S_DN_D$, $S_DN_E$, $S_EN_D$, and $S_EN_E$ respectively. Between the four configuration sets, there is considerable amount of clone pairs shared between two adjacent sets (as depicted in \Cref{fig:good-ok-pairs}), but there is no clone pair that is agreed by all four combinations.

@@

\begin{table}
	\centering
	\caption{The number of disagreed online clone pair condidates before and after filtering.}
	\label{tab:online_clone_pairs}
	\small
	%	\resizebox{\columnwidth}{!}{%
	\begin{tabular}{l|r|c|c|c|c|r}
		\hline
		\multirow{2}{*}{Set} & \multirow{2}{*}{Before Filters} & \multicolumn{4}{c|}{Filters*} & \multirow{2}{*}{After Filters} \\ \cline{3-6}
		& & \textit{L} & \textit{S} & \textit{R} & \textit{G} & \\
		\hline 
		%		\multirow{1}{*}{\textit{good}} & 2,308 & & & & & 2,308 \\
		%		\multirow{1}{*}{\textit{ok}} & 11,749 & & & & & 11,749 \\
		%\multirow{1}{*}{\textit{agreed clone pairs}}      & 29,099 \\
		\multirow{1}{*}{$S_D$} & 67,570 & \checkmark & & \checkmark & \checkmark & 17,801 \\
		\multirow{1}{*}{$N_D$} & 632,855 & & \checkmark & \checkmark & \checkmark & 88 \\ 
		%\multirow{1}{*}{\textit{disagreed clone pairs}}    & 1,039 \\
		\hline
		Total  & 6,400,425 & \multicolumn{4}{c|}{ } & 17,169 \\ 
		\hline
		\multicolumn{7}{l}{Filters*: \textit{L}=clone line $\geq 10$, \textit{S}=similarity $\geq 85\%$,}  \\
		\multicolumn{7}{l}{\textit{R}=regular expressions, and \textit{G}=\textit{good}/\textit{ok} pairs.} \\
	\end{tabular} %
	%}
\end{table}

The disagreed clone pairs are clone pairs that are reported by a single tool, either Simian or NiCad, and do not have agreement from the other tool. The disagreement can be from a misalignment of clone lines or totally non-overlapping clones. The disagreed pairs from Simian cover clone pairs in the projects with NiCad's errors (1 projects from $N_D$ and 5 from $N_E$). %that are automatically missing from the agreed clone pairs. 
With the four configuration combinations, we decided to investigate only $S_D$, and $N_D$, and dropped $S_E$ and $N_E$ due to their enormous amount of clone pairs (60 and 250 millions respectively). Moreover, $S_E$ and $N_E$ contain a large number of false positives due to the recall preference of their EvaClone configurations.

Even choosing only the default configurations, the number of clone pair candidates are still very large for manual inspection (67,570 for $S_D$ and 632,855 pairs for $N_D$). We applied four filters: \textbf{clone line, regular expression, similarity threshold, and good/ok pairs}. For the clone line filter, we raised the minimum clone size to 10 line since larger clones are more interesting, while smaller ones tend to be false clones~\cite{Saini2016}. Moreover, the study of uniqueness of source code by Gabel and Su~\cite{Gabel2010} suggests that source code are unique when they are larger than seven lines. Since the 10--line threshold is already the default configuration for NiCad, this filter is applied to Simian only (Simian's default configurations has a minimum clone size of 6 lines).~The regular expression filter removes boiler-plate clones of \verb|hashCode()| methods and getters/setters. The third filter, similarity threshold, applies only to NiCad clone pairs since Simian does not provide this similarity configuration. The last filter, good/ok pairs, removes the clone pairs that have already existed in the agreed clone sets.

\begin{table}
	\centering
	\caption{The number of online clones candidates for the classification}
	\label{tab:online_clone_classification_results}
	\small
	%	\resizebox{\columnwidth}{!}{%
	\begin{tabular}{l|r|r|r}
		\hline
		\multirow{2}{*}{Set} & \multirow{2}{*}{Candidates} & \multicolumn{2}{c}{Classification} \\ \cline{3-4}
		& & Auto & Manual \\
		\hline 
		\multirow{1}{*}{\textit{good}} & 2,308 & 10 & 2,298 \\
		\multirow{1}{*}{\textit{ok}} & 11,749 & 11,494 & 255 \\
		%\multirow{1}{*}{\textit{agreed clone pairs}}      & 29,099 \\
		\multirow{1}{*}{$S_D$} & 17,801 & 16,800 & 1,001 \\
		\multirow{1}{*}{$N_D$} & 88 & 10 & 78 \\ 
		%\multirow{1}{*}{\textit{disagreed clone pairs}}    & 1,039 \\
		\hline
		Total  & 31,946 & 28,314 & 3,632 \\ 
		\hline
	\end{tabular} %
	%}
\end{table}

As shown in \Cref{tab:online_clone_pairs}, for $S_D$ we filtered the results using clone size, regular expressions, and gook/ok pairs. The three filters reduced the number of $S_D$ clones to 17,801 pairs. 
%For $N_D$, 10-line threshold is already a minimum NiCad's clone size. However, NiCad still reported much more clone pairs than Simian since it can detect type-3 clones. Thus, besides regular expressions and good/ok pair filters, 
We filtered $N_D$ clones by raising the similarity threshold. We increase NiCad's similarity threshold from 70\% to 85\% (by adjusting NiCad's $\mathrm{UPI}$ parameter from 0.3 to 0.15). We tried varying the UPI from 70\% (default), 80\%, 85\% and 90\% and found that 85\% similarity provided the best balance in terms of the amount of reported clones and feasibility for manual investigation. Using this filter along with the regular expression and the good/ok pair filter, we reduced the size of $N_D$ clones to 88 pairs.

%In our clone classification process, we used a script to automatically classify {\small\texttt{equals()}} clone pairs which helped classifying 28,444 pairs out of 31,946 (more than half of the {\small\texttt{equals()}} pairs came from \textit{ok} and $S_D$ pairs). Finally, there are 3,502 pairs remaining which we manually classified them. The classification summary is shown in \Cref{tab:online_clone_classification_results}.
